### 2023-10-16 README.Rmd
update readme with link to published paper

This repository contains the code and data necessary to reproduce the main results of the preprint ["Sentinel lead pipe racks quantify orthophosphate’s dose-response in drinking water"](https://doi.org/10.26434/chemrxiv-2023-h1459).

>>>>

This repository contains the code and data necessary to reproduce the main results of the paper ["Evaluating sentinel pipe racks for monitoring lead release and optimizing corrosion control"](https://doi.org/10.1021/acsestwater.3c00273) (also available as a [preprint](https://doi.org/10.26434/chemrxiv-2023-h1459-v3)).
